Response to the defense feedback

### 2021-06-03 Chapter-3/Chapter-3.tex
Updates from Overleaf

\section{Evaluation}
We evaluate our method on real-world crypto libraries, which include  OpenSSL, mbedTLS, Libgcrypt and Monocypher\@. OpenSSL is the most commonly used crypto libraries in today's software. mbedTLS\@ (previous known as PolarSSL) is designed to be easy to understand and fit on embedded devices. We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
According to the developers, Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model. Libgcrypt is a cryptographic library from the GunPG. As some previous work (e.g., CacheD) choose to evaluate their tools on Libgcrypt, we can compare the evaluation results by applying the tool on Libgcrypt.

@@

We also evaluate our tool on the RSA implementation. With the optimization
introduced in the previous sections, we need not apply domain knowledge to
simplify the analysis. Our tool identifies all leakage sites
reported by CacheD~\cite{203878} and find new leaks in less time.
We also find newer versions of RSA in OpenSSL have fewer leaks. Our tool can
finish all the analysis in less than 6 hours.

@@

In this section, we compare \detect{} with the
existing trace-based side-channel detection tools on vulnerability detections. For other tools, we use the reported results in their papers. As other tools do not quantify leakage sites, we only include the time of detecting vulnerabilities to perform a fair comparison.

The comparison result with CacheD~\cite{203878} is shown in Table~\ref{eval:cacheD}.
Note that one statement in the source code can be compiled into several machine instructions. So it is possible that one statement can have multiple leakage points. Under the circumstance, we think it is only a leakage.
We have confirmed that \detect{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \detect{} finds many new ones.
CacheD fails to detect some vulnerabilities for two
reasons. First, CacheD can only detect secret-dependent data access
vulnerabilities. \detect{} can detect secret-dependent control-flows as well.
Second, according to the CacheD paper, CacheD times out after 20 hours to process
asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
the analysis.
While these optimizations do not introduce false positives, they may miss some
vulnerabilities.
Third, CacheD only symbolizes the encryption keys. Some side-channel leakages when the input messages equal to some certain values. It is possible that CacheD miss some
leakages as we have discussion the previous sections.
We notice that the number of instructions in these traces are different due to the different analysis starting functions and building options during the evaluation.
Table~\ref{eval:cacheD} shows that
\detect{} is faster than CacheD. \detect{} is much faster than CacheD when analyzing the same
number of instructions. For example, when we test~\detect{} on AES from OpenSSL
0.9.7, \detect{} is over 100x faster than CacheD.
\begin{table*}[ht]
 \centering
  \caption{Comparison with CacheD: Time,
    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
  \label{eval:cacheD}

>>>>

\section{Evaluation}
We evaluate our method on real-world crypto libraries, which include  OpenSSL, mbedTLS, Libgcrypt and Monocypher\@. OpenSSL is the most commonly used crypto libraries in today's software. mbedTLS\@ (previous known as PolarSSL) is designed to be easy to understand and fit on embedded devices. We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
According to the developers, Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model. Libgcrypt is a cryptographic library from the GunPG. As some previous work (e.g., CacheD) choose to evaluate their tools on Libgcrypt, we can compare the evaluation results by applying our tool on Libgcrypt.

@@

We also evaluate our tool on the RSA implementation. With the optimization
introduced in the previous sections, we need not apply domain knowledge to
simplify the analysis. Our tool identifies all leakage sites
reported by CacheD~\cite{203878} and find a new leak in shorter time.
We also find newer versions of RSA in OpenSSL have fewer leaks. Our tool can
finish all the analysis in less than 6 hours.

@@

In this section, we compare \detect{} with the
existing trace-based side-channel detection tools on vulnerability detections. For other tools, we use the reported results in their papers~\cite{203878}. As other tools do not quantify leakage sites, we only include the time of detecting vulnerabilities to perform a fair comparison.

The comparison result with CacheD~\cite{203878,217537} is shown in Table~\ref{eval:cacheD}.
Note that one statement in the source code can be compiled into several machine instructions. So it is possible that one statement can have multiple leakage points. In the circumstance, we consider it takes only one leakage.
We have confirmed that \detect{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \detect{} finds many new ones.
CacheD fails to detect some vulnerabilities for two
reasons. First, CacheD can only detect secret-dependent data access
vulnerabilities. \detect{} can detect secret-dependent control-flows as well.
Second, according to the CacheD paper, CacheD times out after 20 hours when processing
asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
the analysis.
While these optimizations do not introduce false positives, they may miss some
vulnerabilities.
Third, CacheD only symbolizes the encryption keys. Some side-channel leakages occurs when the input messages equal to some certain values. It is possible that CacheD misses some
leakages as we have discussion the previous sections.
We notice that the number of instructions in these traces are different due to the different analysis starting functions and build options during the evaluation.
Table~\ref{eval:cacheD} shows that
\detect{} is faster than CacheD. \detect{} is much faster than CacheD when analyzing the same
number of instructions. For example, when we test~\detect{} on AES from OpenSSL
0.9.7, \detect{} is over 100x faster than CacheD.
\begin{table*}[ht]
 \centering
  \caption{Comparison with CacheD: Time,
    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
  \label{eval:cacheD}
